---
title: "Assingment NYC Flight Data"
author: "Yonit Marcus"
date: "October 5, 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, `airports.csv`, `planes.csv` and `weather.csv`.  Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}

## tried both readr as well as read.csv
flights2 <- readr::read_csv('c:/csx460_rep/csx460/02-fundamentals/data/flights.csv')

flights <- read.csv("C:/csx460_rep/CSX460/02-fundamentals/data/flights.csv",stringsAsFactors = FALSE)















```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

hist(flights$arr_delay, main = "Histogram of arrival delays",
+      xlab = "Arrival Delay (mins)")

 hist(flights$dep_delay, main = "Histogram of departure delays",
+      xlab = "Departure Delay (mins)")


```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}

plot(x = as.Date(flights[,19]), y = flights$arr_delay,
+      main = "Date vs. Arrival Delay",
+      xlab = "Date",
+      ylab = "Arrival Delay (mins)")

```



## Create tables for Categorical Variables

Create a `table` of occurences of origin airports and carrier.

```{r}

 table(flights[c("carrier","origin")])


```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}


airports <- read.csv("C:/csx460_rep/CSX460/02-fundamentals/data/airports.csv",stringsAsFactors = FALSE)
   
 planes <- read.csv("C:/csx460_rep/CSX460/02-fundamentals/data/planes.csv",stringsAsFactors = FALSE)
  
weather <- read.csv("C:/csx460_rep/CSX460/02-fundamentals/data/weather.csv",stringsAsFactors = FALSE)
detailed_flights<-dplyr::left_join(flights,planes, by = "tailnum")
detailed_flights<-dplyr::left_join(detailed_flights,airports, c("dest" = "faa"))
detailed_flights<-dplyr::left_join(detailed_flights,airports, c("origin" = "faa"))

```



