---
title: "NYCFlights: Arrival Delay Regression Model"
author: "Yonit Marcus"
date: "10/17/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(magrittr)
library(stringr)
library(dplyr)
library(data.table)
```

# NYCFlights Model

Using the rectangular data that you created last week and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay. Follow MLwR structure 
for building a model. Describe/Explain each of the steps and show all work in codeblocks below.


## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
flights <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/flights.csv')
planes <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/planes.csv')
airports <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/airports.csv')
weather <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/weather.csv')
YX<-left_join(flights,weather,by=c("origin","year","month","day","hour"))
YX<-left_join(YX,planes, by = "tailnum")
YX<-left_join(YX,airports, c("dest" = "faa"))
YX<-left_join(YX,airports, c("origin" = "faa"))
YX$tailage=YX$year.x-YX$year.y
```



## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }
## plotting response distrbution
hist(YX$arr_delay)

pairs(YX[c("arr_delay","dep_delay","distance","air_time","engines","wind_dir","wind_speed","seats")])
 cor(flights$arr_delay,flights$dep_delay,use="complete")
## cor between dep_delay and arr_delay is 0.914
  
  aggdata <-aggregate(data=flights, arr_delay~carrier, 
   FUN=mean, na.rm=TRUE)
```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }

## Naive model - use only departue delay

delay_model_simple=lm(arr_delay~dep_delay,data=YX)
delay_model=lm(arr_delay~dep_delay+air_time+distance+temp+dewp+humid+wind_dir+wind_speed+wind_gust+pressure+seats+tailage,data=YX)


```

## Step 4: Evaluate Performance

Evaluating performance is a crutial step, that has yet to be treated well by the MLwR. Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }
summary(delay_model_simple)
# Multiple R-squared:  0.8369. Residual standard error: 18.03
summary(delay_model)
# Multiple R-squared:  0.8755. Residual standard error: 14.94
```


## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }
YX$dist_sqr=YX$distance^2
delay_model_v1=lm(arr_delay~dep_delay+air_time+distance+temp+dewp+humid+wind_dir+wind_speed+wind_gust+pressure+seats+tailage+dist_sqr,data=YX)
summary(delay_model_v1)
# Multiple R-squared:  0.8761. Residual standard error: 14.9
delay_model_v2=lm(arr_delay~dep_delay+air_time+distance+temp+dewp+humid+wind_dir*wind_speed+wind_gust+pressure+seats+tailage+dist_sqr+carrier+origin*dest,data=YX)
summary(delay_model_v2)
# Multiple R-squared:  0.8919. Residual standard error: 13.92
```


# Question:

Is this a good model?  (Write your answer here.)

Yes, good correlation between the model prediction and the response

