---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "[Your Name]"
date: "[Today's Date]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(ggplot2)
library(magrittr)
library(stringr)
library(dplyr)
library(data.table)
```


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.
p9 <- ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
        stat_function(fun = dnorm)
- Plot the logistic function from  `[-10,10]`

- Write a R function for the8 inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }


logistic_func <- function(x_arr) {
  res<-c()
  for(i in 1:length(x_arr)) {
   res[i]<-1/(1+exp(x_arr[i]*-1))
  }
  return(res)
}

logit_func <- function(y_arr) {
  res<-c()
  for(i in 1:length(y_arr)) {
   res[i]<-log(y_arr[i])-log(1-y_arr[i])
  }
  return(res)
}

curve(logistic_func(x), -10, 10, n = 101, add = FALSE, type = "l")
curve(logit_func(x), 0, 1, n = 101, add = FALSE, type = "l")

```


# NYCFlights Model

Using the rectangular data that you created from assignment and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay >= 15 minutes. Follow *MLwR* structure   for building a model. Describe/Explain each of the steps and show all work in codeblocks below.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.   

## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
flights <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/flights.csv')
planes <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/planes.csv')
airports <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/airports.csv')
weather <- read_csv('c:/csx460_rep/csx460/02-fundamentals/data/weather.csv')
YX<-left_join(flights,weather,by=c("origin","year","month","day","hour"))
YX<-left_join(YX,planes, by = "tailnum")
YX<-left_join(YX,airports, c("dest" = "faa"))
YX<-left_join(YX,airports, c("origin" = "faa"))

```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: prep data" }
YX$tailage=YX$year.x-YX$year.y
YX_LOG<-YX
YX_LOG$arr_delay_gt_15 <-ifelse(YX_LOG$arr_delay >= 15, 1, 0)

```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }

form <- arr_delay_gt_15 ~ dep_delay+air_time+distance+temp+dewp+humid+wind_dir+wind_speed+wind_gust+pressure+seats+tailage
fit <- glm( form, family = binomial(logit),  YX_LOG %>% sample_n(1000) )

```

## Step 4: Evaluate Performance

Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }
test_data<-sample_n(YX_LOG,10000)
test_data$prediction<-predict(fit,test_data,type="response")
test_data$prediction_class<- ifelse(test_data$prediction > 0.5,1,0)
mean(ifelse(is.na(test_data$prediction_class),0,ifelse(test_data$prediction_class==test_data$arr_delay_gt_15,1,0)) )

```

 
## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }

```


# Question:

Is this a good model?  (Write your answer here.)
Precision is 0.65 - not bad but could be better

# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

