---
title: "Classification Metrics"
author: "Yonit Marcus"
date: 11/7/2016
output: html_document
---

The German Credit Data (data/german_credit); 

1. Read in the German Credit Data
2. Partition the model into Test and Training Sets using only `base::sample` 
3. Train a model for `Creditability` 
4. Knit the document and submit both the this file Rmd and html files.

Show All Work! 

```{r}
library(readr)
library(ggplot2)
library(magrittr)
library(stringr)
library(dplyr)

credit_data <- read_csv('c:/csx460_rep/csx460/data/german_credit.csv')
random_ind=sample(1:1001,100)
test<-credit_data[random_ind,]
train<-credit_data[-random_ind,]
credit_model=glm(Creditability~.,family = binomial(logit),data=train)

```


Using the `predict` function and `test` data, write functions to calculate and 
calculate: 

* Misclassification Rate
* Prevalence 
* Accuracy
* Accuracy
* Error Rate / Misclassification Rate
* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision

```{r}
test$prediction<-predict(credit_model,test,type="response")
test$prediction_class<- ifelse(test$prediction > 0.5,1,0)
credit_pred<-predict(credit_model,test,type="response")
accuracy<-(sum(test$prediction_class==test$Creditability)/100)
# accuracy = 84%
error_rate<-1-accuracy
# Err Ratte = 16%
TP <- sum(test$prediction_class==1 & test$Creditability==1)
TN <- sum(test$prediction_class==0 & test$Creditability==0)
FP <- sum(test$prediction_class==1 & test$Creditability==0)
FN <- sum(test$prediction_class==0 & test$Creditability==1)
OP = sum(test$Creditability==1)
ON=sum(test$Creditability==0)
TPR<-TP/OP
# TPR (Sensitivity,Recall) = 93.5%
FPR <-FP/ON
#FPR = 47.8%
TNR <-TN/ON
#TNR, Specificity = 52.1%
Precision <-TP/(TP+FP)
# Precision = 86.7%
```
